---
title: "Using crewargs"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Using crewargs}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```


## Example: Workers with modified `max-connections`

Suppose you want to create a {targets} "makefile" with workers that have access to
an increased number of connections.  R accepts a command line argument `--max-connections=321`, but how do we get that passed to the workers?


```{r, eval=FALSE}
# save this to _targets_example.R
library(targets)
library(crewargs)

tar_option_set(
  packages = c("crewargs"), 
  controller = 
    crewargs_controller_local_args(
      workers = 2, seconds_idle = 60, 
      cmdargs = "--max-connections=321"
    )
)

list(
  tar_target(
    name = connections, command = parallelly::availableConnections()
  )
)
```

```{r, include=FALSE}
cat(file = "_targets_example.R",
'
library(targets)
library(crewargs)

tar_option_set(
  packages = c("crewargs"), 
  controller = 
    crewargs_controller_local_args(
      workers = 2, seconds_idle = 60, 
      cmdargs = "--max-connections=321"
    )
)

list(
  tar_target(
    name = connections, command = parallelly::availableConnections()
  )
)
'
)
```

```{r, results = 'hide'}
tar_make(
  script = "_targets_example.R",
  callr_arguments = list(
    'cmdargs' = c("--save", "--no-save", "--no-restore", "--max-connections=400")
  )
)
```

The number of connections available to workers (321) is determined by `cmdargs` 
passed to the controller, not by `cmdargs` passed to `callr::r()`.

```{r}
tar_read(connections)
```
